---
title: "Project Kaleidoscope Assignment 1"
output:
  html_document: default
  pdf_document: default
---

Getting and setting working directory
```{r}
rm(list=ls())
getwd()
setwd("C:/Users/sonia mehra/Desktop/Kaleidoscope")
```

```{r setup, include=FALSE}
library(plyr)
library(dplyr)
library(ggplot2)
library(readxl)
library(plotly)
knitr::opts_chunk$set(echo = TRUE)
```

Loading data   
Loading only 1388 rows since last two rows have incomplete data.NIFTY data is also loaded side in variable data_nifty and combining both the data in combined_data.The thing which is to be observed is data and data1 have same date order so data_nifty dates are not added in combined_data because they coincide with data date.759 and 760 row are removed because they have incomplete data 
```{r}
data=read_excel("Data for Assignment_1.xlsx")
data=as.data.frame(data)
data=data[1:1388,]
data$Date=as.Date(data$Date)

data_nifty=read_excel("Data for Assignment_1.xlsx",sheet = "NIFTY50")
data_nifty=as.data.frame(na.omit(data_nifty))
data_nifty$Date=as.Date(data_nifty$Date)

combined_data=cbind(data,NIFTY=data_nifty[,2])
combined_data=combined_data[-c(759,760),]
```

## Part 1
Yearly returns
```{r}
start=c("2014-04-01","2015-04-01","2016-04-01","2017-04-03","2018-04-02")
end=c("2015-04-01","2016-04-01","2017-04-03","2018-04-02","2019-04-01")

year_return=data.frame(company=colnames(combined_data)[-1])
i=1
while(i<=5){
  x=as.matrix(as.numeric(combined_data%>%filter(Date==start[i])))
  y=as.matrix(as.numeric(combined_data%>%filter(Date==end[i])))
  year_return=cbind(year_return,((y-x)/x)[2:13,])
  i=i+1
}
colnames(year_return)[-1]=c(2014,2015,2016,2017,2018)
row.names(year_return)<-colnames(combined_data)[-1]
year_return$company<-NULL
print(year_return)
```

## Part 2
Correlation between securities.Calculaton of return and then calculation of correlation.
```{r}
return_rate=data.frame(S.No=seq(1,1385))
for (i in seq(2,13)){
  combined_data[,i]=as.numeric(combined_data[,i])
  return_rate=cbind(return_rate,-diff(combined_data[,i])/combined_data[,i][-1])}
return_rate=na.omit(return_rate)
colnames(return_rate)=colnames(combined_data)
return_rate$Date=NULL
cor(return_rate[,1:11])
```
The one with highest correlation is `r colnames(data)[6]` and `r colnames(data)[8]`
and The one with lowest correlation is `r colnames(data)[2]` and `r colnames(data)[11]`

## Part 3
Plotting Yearly return for all securities
```{r}
year_return=data.frame(t(year_return))
ggplotly(ggplot(data=year_return,aes(x=c(1,2,3,4,5),xlab="Year"))+
 geom_line(aes(y=year_return[,1],colour=colnames(year_return)[1]))+
  geom_line(aes(y=year_return[,2],colour=colnames(year_return)[2]))+
  geom_line(aes(y=year_return[,3],colour=colnames(year_return)[3]))+
  geom_line(aes(y=year_return[,4],colour=colnames(year_return)[4]))+
  geom_line(aes(y=year_return[,5],colour=colnames(year_return)[5]))+
  geom_line(aes(y=year_return[,6],colour=colnames(year_return)[6]))+  
  geom_line(aes(y=year_return[,7],colour=colnames(year_return)[7]))+
  geom_line(aes(y=year_return[,8],colour=colnames(year_return)[8]))+
  geom_line(aes(y=year_return[,9],colour=colnames(year_return)[9]))+
  geom_line(aes(y=year_return[,10],colour=colnames(year_return)[10]))+
  geom_line(aes(y=year_return[,11],colour=colnames(year_return)[11]))+
  geom_line(aes(y=year_return[,12],colour=colnames(year_return)[12]))+
  labs(x="year 1-2014 5-2019",y="Yearly Return"))

```

Observation:  For year 
(i)2014 LT MIDCAP FUND has highest return
(ii)2015 SBI MAGNUM MIDCAP has highest return 
(iii)2016 LTMIDCAP FUND has highest return
(iv)2017 SBI FOCUSSED EQUITY FUND has highest return
(v)2018 NIFTY has highest return

## Part 4
Diversification Ratio
```{r}
ret=return_rate[,1:11]
ret$Portfolio=rowMeans(ret)  
st_dev=apply(ret, 2, sd) 
for (i in 1:11){print(1/(st_dev[i]/st_dev[12]))}
```
Security with lowest Diversification Ratio is NIPPON INDIA LARGECAP FUND so it will give Higher Diversification Benifits

## Part 5
Security to be added to the Portfolio
```{r}
quantity=c(87456.32367,180234.3633,182973.050)
w=quantity/sum(quantity)
Port=combined_data[seq(1145,1386),c(1,3,4,8)]

Port_return=data.frame(S.No=seq(1,241))
for (i in seq(2,4)){
  Port_return=cbind(Port_return,-diff(Port[,i])/Port[,i][-1])}
Port_return$S.No<-NULL
colnames(Port_return)<-colnames(Port)[-1]

R_p=sum(((Port[1,][-1]-Port[242,][-1])/(Port[242,][-1]))*w)
R_f=0.0291
weighted_return=rep(0,241)
for (i in seq(1,241)){
weighted_return[i]=weighted.mean(Port_return[i,],w)}
sd_portfolio=sd(weighted_return)
Sharpe_portfolio=(R_p-R_f)/(sd_portfolio*sqrt(242))

asset=combined_data[seq(1145,1386),c(1,2,5,6,7,9,10,11,12)]

asset_return=data.frame(S.No=seq(1,241))
for (i in seq(2,9)){
  asset_return=cbind(asset_return,-diff(asset[,i])/asset[,i][-1])}
asset_return$S.No<-NULL
colnames(asset_return)<-colnames(combined_data)[c(2,5,6,7,9,10,11,12)]

sd_asset=apply(asset_return,2,sd)
R_p=(asset[1,][-1]-asset[242,][-1])/(asset[242,][-1])
R_f=0.0291
Sharpe_asset=(R_p-R_f)/(sd_asset*sqrt(242))

RHS=cor(asset_return,weighted_return)*Sharpe_portfolio
Sharpe_asset>RHS
```
All the securities with TRUE under them should be added to Portfolio.Most preferable among all of them is the one with highest Sharpe ratio i.e.`r colnames(asset_return)[which.max(Sharpe_asset)]`.

## Part 6

Best Portfolio among all of the randomly selected portfolio 
```{r}
Sharpe_portfolio=rep(NA,3)
b=rep(NA,3)
for (i in seq(1,3)){a=sample(seq(2,12),3,replace=F)
b=rbind(b,a)
Port=combined_data[seq(1145,1386),c(1,a)]

Port_return=data.frame(S.No=seq(1,241))
for (j in seq(2,4)){
  Port_return=cbind(Port_return,-diff(Port[,j])/Port[,j][-1])}
Port_return$S.No<-NULL
colnames(Port_return)<-colnames(Port)[-1]

R_p=sum(((Port[1,][-1]-Port[242,][-1])/(Port[242,][-1]))*(1/3))
R_f=0.0291
sd_portfolio=sd(apply(Port_return,1,mean))
Sharpe_portfolio[i]=(R_p-R_f)/(sd_portfolio*sqrt(242))}
b=na.omit(b)
print(Sharpe_portfolio)
BEST=b[which.max(Sharpe_portfolio),]
colnames(combined_data)[BEST]
```
The best portfolio among all of the randomly selected portfolio is `r colnames(combined_data)[BEST]`