---
title: "Assignment 2"
author: "Sonia Mehra"
date: "01/07/2020"
output: html_document
---

Getting and setting working directory
```{r}
rm(list=ls())
getwd()
setwd("C:/Users/sonia mehra/Desktop/Kaleidoscope")
```

Loading data   
Loading only 1388 rows since last two rows have incomplete data.NIFTY data is also loaded side in variable data_nifty and combining both the data in combined_data.The thing which is to be observed is data and data1 have same date order so data_nifty dates are not added in combined_data because they coincide with data date.759 and 760 row are removed because they have incomplete data.Moreover data from 1 April 2014 to 31 March 2019 is taken into consideration.
```{r}
library(readxl)
data=read_excel("Data for Assignment_2.xlsx")
data=as.data.frame(data)
data=data[1:1388,]
data$Date=as.Date(data$Date)

data_nifty=read_excel("Data for Assignment_2.xlsx",sheet = "NIFTY50")
data_nifty=as.data.frame(na.omit(data_nifty))
data_nifty$Date=as.Date(data_nifty$Date)

combined_data=cbind(data,NIFTY=data_nifty[,2])
combined_data=combined_data[-c(759,760),]
combined_data=combined_data[seq(162,1386),]

```

## Part 2
Calculation of returns from price and then calculation of standard deviation
```{r}
return_rate=data.frame(S.No=seq(1,1224))
for (i in seq(2,13)){
  combined_data[,i]=as.numeric(combined_data[,i])
  return_rate=cbind(return_rate,-diff(combined_data[,i])/combined_data[,i][-1])}
return_rate=na.omit(return_rate)
colnames(return_rate)=colnames(combined_data)
return_rate$Date=NULL

st_dev=apply(return_rate,2,sd)
print(st_dev)
min_st_dev=st_dev[which.min(st_dev)]
print(min_st_dev)
```
The security with lowest standard deviation is SBI FOCUSSED EQUITY FUND 

## Part 3

Standard deviation of Portfolio
```{r}
portfolio=apply(return_rate[,1:11],1,mean)
sd(portfolio)
```
Standard Deviation of Portfolio is lower than Lowest standard deviation therefore decrease in risk
## Part 4

Beta and adjusted beta for all securities using 2 approaches covariance approach and regression approach    
**Beta using Covariance approach**
```{r}
var_market=var(return_rate$NIFTY)
beta=rep(0,11)
adj_beta=rep(0,11)
for (i in seq(1,11)){
  covariance=cov(return_rate[,i],return_rate$NIFTY)
  beta[i]=covariance/var_market
  adj_beta[i]=(1/3)+(2/3)*beta[i]
}
beta_data_frame=data.frame(colnames(return_rate)[1:11],beta,adj_beta)
print(beta_data_frame)
```
**Beta using regression approach**
```{r}
beta_alter=rep(0,11)
for (i in seq(1,11)){
 beta_alter[i]=lm(return_rate[,i]~return_rate$NIFTY)$coefficients[2]
}
print(beta_alter)
```
Beta using regression approach is same as beta using covariance approach

## Part 5

Value at Risk of portfolio using 2 methods analytical method and Historic Simulation method   
**Analytical Method**
```{r}
m=mean(portfolio)
s=sd(portfolio)
VAR_1=m-1.645*s
print(VAR_1)
```
**Historic Simulation Method**
```{r}
VAR_2=sort(portfolio)[round(0.05*1382)]
print(VAR_2)
```
VAR using two approaches is same upto two places of decimal



